TBD

### 2021-03-08 outputs/paper/paper.Rmd
updade model

```{r regression, echo=FALSE, warning=FALSE, fig.width=8, fig.height=7}
library(fastDummies)
Dummy_data<- fastDummies::dummy_cols(FS, remove_first_dummy = TRUE, remove_selected_columns = TRUE)%>%
  select(-c(2:4))#  change categorical var to factors

>>>>

```{r regression, echo=FALSE, warning=FALSE, fig.width=8, fig.height=7}

## transfer data into dummy
library(fastDummies)
Dummy_data<- fastDummies::dummy_cols(FS, remove_first_dummy = TRUE, remove_selected_columns = TRUE)%>%
  select(-c(2:4))#  change categorical var to factors

##create model
model <- lm(post_favor_Sanders ~., data =Dummy_data )
summary(model)
```
